--- 
title: "A Book With Skills For Researchers"
author: "Jenny Lee"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
documentclass: book
bibliography:
- book.bib
- packages.bib
description: |
  This is a minimal example of using the bookdown package to write a book.
  set in the _output.yml file.
  The HTML output format for this example is bookdown::gitbook,
link-citations: yes
github-repo: rstudio/bookdown-demo
---

# About

This book contains introduction to Git and Github, how to build a R package, how to build a bookdown.

## How I created this bookdown? 

I first started from following a Youtube tutorial: <https://www.youtube.com/watch?v=RdSmYvbQkhs&t=192s>

A creation of **bookdown** is done by **bookdown** package [@R-bookdown]. So I started to read a tutorial of **bookdown** package [@bookdown2016] for the detailed explanation : <https://bookdown.org/yihui/bookdown/>

### Gitbook template
The easiest way to get started writing a new `gitbook` is to use the RStudio Project Wizard (*File > New Project > New Directory > Book project using bookdown*) and select `gitbook` from the dropdown menu. <https://bookdown.org/yihui/bookdown/html.html#fig:new-bs4-book>

- This will create several files such as .Rmd, .yml, .bib to build a template bookdown.

### Initialize git
We initialize this **bookdown** with git, so that we can take advantage of version control and upload in Github.
```{bash, eval=F}
git init
git add --all
git commit -m "Initial bookdown template"
```

### Change .yml files
- In `output.yml` file, there are three sections as below. We would only like to keep  
`bookdown::gitbook:` command but want to comment out `bookdown::pdf_book:` and `bookdown::epub_book: default`. This is how my `output.yml` will look like after commenting out unnecessary lines. This is because, to render this example to PDF as a `bookdown::pdf_book`, you'll need to install XeLaTeX. You are recommended to install TinyTeX (which includes XeLaTeX): <https://yihui.org/tinytex/>.

```{bash, eval=F}
bookdown::gitbook:
  css: style.css
  config:
    toc:
      before: |
        <li><a href="./">A Minimal Book Example</a></li>
      after: |
        <li><a href="https://github.com/rstudio/bookdown" target="blank">Published with bookdown</a></li>
     edit: https://github.com/jennyjyounglee/Analysis_Bookdown/edit/BRANCH/%s
     download: ["pdf", "epub"]
# bookdown::pdf_book:
#   includes:
#     in_header: preamble.tex
#   latex_engine: xelatex
#   citation_package: natbib
#   keep_tex: yes
# bookdown::epub_book: default

```

- In `_bookdown.yml` file, we need to add two of the followings:
  * `book_filename: "Analysis_Bookdown"`
  * `output_dir: "docs"`
  This is how my `_bookdown.yml` will look like after adding the above two lines.

```{bash, eval=F}
book_filename: "Analysis_Bookdown"
delete_merged_file: true
output_dir: "docs"
language:
  ui:
    chapter_name: "Chapter "
```

We again commit the changes we made on `_output.yml` and `_bookdown.yml` files.
```{bash, eval=F}
git status
git add _bookdown.yml
git add _output.yml
git commit -m "Change bookdown output defaults"
```

### Render a book

You can render the HTML version of this example book without changing anything:

In Rstudio > Build > Build Book. i.e. Find the **Build** pane in the RStudio IDE, and click on **Build Book**, then select your output format, or select "All formats" if you'd like to use multiple formats from the same book source files.

Or build the book from the R console:
```{r, eval=FALSE}
bookdown::render_book()
```

This will create two folders `/docs` and `_bookdown_files`.
- `/docs` contains .html file created from .Rmd files
- `bookdown_files` contains complied images, which we don't need to commit image files. So we add a line `bookdown_files` in `.gitignore`. This is how my `.gitignore` file looks like.
```{bash, eval=F}
.Rproj.user
.Rhistory
.RData
.Ruserdata

_bookdown_files
```

We again commit the changes we made on `.gitignore` and `docs/` files.
```{bash, eval=F}
git add .gitignore
git add docs/
git commit -m "Ignore bookdown files created on build"
```

### Push to Github
- First, we need to create a repo in Github
- Create a repo name "Analysis_Bookdown" in Github: https://github.com/jennyjyounglee/Analysis_Bookdown
- Then, run the below code to push local repo to Github.
```{bash, eval=F}
git remote add origin https://github.com/jennyjyounglee/Analysis_Bookdown.git
git branch -M main
git push -u origin main
```

### Publish the website!
- In Github > Analysis_Bookdown repo > Settings > Pages > Source/Master/Docs/
- Then your website should be available through <https://jennyjyounglee.github.io/Analysis_Bookdown>


## Usage
Each **bookdown** chapter is an .Rmd file, and each .Rmd file can contain one (and only one) chapter. A chapter *must* start with a first-level heading: `# A good chapter`, and can contain one (and only one) first-level heading.

Use second-level and higher headings within chapters like: `## A short section` or `### An even shorter section`.

The `index.Rmd` file is required, and is also your first book chapter. It will be the homepage when you render the book.

## Preview book

As you work, you may start a local server to live preview this HTML book. This preview will update as you edit the book when you save individual .Rmd files. You can start the server in a work session by using the RStudio add-in "Preview book", or from the R console:

```{r eval=FALSE}
bookdown::serve_book()
```


## How to cite?
A BibTeX database is a plain-text file (with the conventional filename extension `.bib`) that consists of bibliography entries like this:
```bibtex
@Manual{R-base,
  title = {R: A Language and Environment for Statistical
    Computing},
  author = {{R Core Team}},
  organization = {R Foundation for Statistical Computing},
  address = {Vienna, Austria},
  year = {2016},
  url = {https://www.R-project.org/},
}
```

There is a helper function `write_bib()` in **knitr** to generate BibTeX entries automatically for R packages. For example, I created this citation [@R-bookdown] by typing `[@R-bookdown]`. I copy and pasted the output rendered from the below code in `.bib` file <https://bookdown.org/yihui/bookdown/citations.html>.
```{r write-bib, comment='', warning=FALSE, eval=F}
# the second argument can be a .bib file
knitr::write_bib(c('bookdown'), '', width = 60)
```


## Output Formats

The `split_by` argument specifies how you want to split the HTML output into multiple pages, and its possible values are:

- `rmd`: use the base filenames of the input Rmd files to create the HTML filenames, e.g., generate `chapter3.html` for `chapter3.Rmd`.
- `none`: do not split the HTML file (the book will be a single HTML file).
- `chapter`: split the file by the a first-level (`#`)  headers.
- `section`: split the file by the a second-level (`##`)  headers.
- `chapter+number` and `section+number`: similar to `chapter` and `section`, but the files will be numbered.

In my `_bookdown.yml`, I added `split_by:section` so that it split the file by the second-level headers.

```{bash, eval=F}
bookdown::gitbook:
  css: style.css
  lib_dir: assets
  split_by: section
  config:
    toc:
      before: |
        <li><a href="./">A Minimal Book Example</a></li>
      after: |
        <li><a href="https://github.com/rstudio/bookdown" target="blank">Published with bookdown</a></li>
    edit: https://github.com/USERNAME/REPO/edit/BRANCH/%s
    download: ["pdf", "epub"]
```
